Hierarchical Learning for Chagas Detection from ECG under Expert-Label Scarcity

### 2025-08-22 contents/abstract.tex
finish introduction

Methods: The 12-lead ECGs were resampled to 400 Hz, bandpass filtered (0.5–45 Hz), and z-score normalized. We used a ResNet architecture model with squeeze-and-excitation (SE) modules for binary classification. To address severe class imbalance and the scarcity of expert-confirmed labels, we applied stratified upsampling and reliability-weighted label smoothing to prioritize expert-confirmed positives over self-reported ones. Model training used an asymmetric loss to further penalize false negatives, optimized with Adam and a OneCycle learning rate schedule. Model selection was based on the Challenge score from an internal hold-out subset.

Results: In stratified cross-validation on the public training data, our approach achieved a Challenge score of [CV-MEAN]. On the hidden validation set, our method received a Challenge score of [VAL-SCORE] (rank [VAL-RANK]).

Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, offering a promising direction for improving detection accuracy and reliability in resource-limited scenarios.

>>>>

Methods: The 12-lead ECGs were resampled to 400 Hz, bandpass filtered (0.5–45 Hz), and z-score normalized. We used a ResNet model integrated with squeeze-and-excitation (SE) modules for binary classification. To address severe class imbalance and the scarcity of expert-confirmed labels, we applied stratified upsampling and reliability-weighted label smoothing to prioritize expert-confirmed positives over self-reported ones. Model training used an asymmetric loss to further penalize false negatives and was optimized with Adam and a OneCycle learning rate schedule. Model selection was based on the Challenge score from an internal hold-out subset.

Results: In cross-validation on the public training data, our approach achieved a Challenge score of [CV-MEAN]. On the hidden validation set, our method received a Challenge score of [VAL-SCORE] (rank [VAL-RANK]).

Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, and highlights potential for improving detection accuracy and reliability in resource-limited scenarios.

### 2025-08-22 contents/introduction.tex
finish introduction

% NOT finished

to write

>>>>

% almost finished

Addressing underdiagnosis of Chagas disease through scalable ECG-based screening is the focus of the 2025 George B. Moody PhysioNet Challenge \cite{goldberger2000physionet, cinc2025}. Enabled by aggregated multi-cohort ECG datasets \cite{ribeiro2020automatic, Cardoso_2016_Sami-Trop, wagner2020ptb_xl, Nunes_2021_Incidence, Filho_2020_Prognostic}, the Challenge frames a multi-source learning setting with heterogeneous label reliability and severe class imbalance.

In this work, we propose a reliability-aware hierarchical framework that prioritizes expert-confirmed labels and mitigates severe class imbalance within a deep ECG model, with optimization aligned to prevalence-constrained sensitivity objectives.
